Markov Chain Monte Carlo (MCMC)

### 2016-05-24 articles/articles.Rmd
logic workflow
completely reorganized

- Labels are for cans not for people. [[Facebook Videos](https://www.facebook.com/morokcom/videos/237500609921393/)]
- Practical Frameworks for Beating Burnout [[First Round Review](http://firstround.com/review/practical-frameworks-for-beating-burnout/?ct=t(How_Does_Your_Leadership_Team_Rate_12_3_2015))]
- Land any job you want. [[blog](http://landanyjobyouwant.com/)]
- The career advice no one tells you. [[Quartz](http://qz.com/640112/the-career-advice-no-one-tells-you/)]
- Wanted in College Graduates: Tolerance for Ambiguity. [[Linkedin Pulse](https://www.linkedin.com/pulse/wanted-college-graduates-tolerance-ambiguity-jeff-selingo)]
- How to set goals: OKRs. [[Youtube](https://www.youtube.com/watch?v=mJB83EZtAjc)]
- Meetings that don’t suck. [[Youtube](https://www.youtube.com/watch?v=rU8nv38E0Qk)]

@@

@@

- Facebook is the new Excel. [[blog](http://alexmuir.com/facebook-is-the-new-excel)]
- We need companies to start innovating instead of imitating success stories. [[Hustle](http://thehustle.co/snapchat-vs-spacex-battle-of-the-imitators-and-innovators)]
- My 4+ Years At Uber Taught Me These Key Lessons. 1. May the supply be with you ; 2. Don't listen, show them. [[Linkedin](https://www.linkedin.com/pulse/three-things-i-learned-during-4-years-uber-michael-pao)]

>>>>

- Reddit and Facebook Veteran On How to Troubleshoot Troublemakers. [[First Round Review](http://firstround.com/review/reddit-and-facebook-veteran-on-how-to-troubleshoot-troublemakers/?ct=t(How_Does_Your_Leadership_Team_Rate_12_3_2015))]
    - Hermits. Get them to collaborate with a team.
    - Nostalgia. Ask qualities that they missed most, and see if there're existing projects that could allow them to recapture that feeling.
    - Trend Chaser. Ask them why this is the route their going to take? The potential has to worth more than the expense of experimenting.
- Labels are for cans not for people. [[Facebook Videos](https://www.facebook.com/morokcom/videos/237500609921393/)]
- Practical Frameworks for Beating Burnout [[First Round Review](http://firstround.com/review/practical-frameworks-for-beating-burnout/?ct=t(How_Does_Your_Leadership_Team_Rate_12_3_2015))]
- Land any job you want. [[blog](http://landanyjobyouwant.com/)]
- The career advice no one tells you. [[Quartz](http://qz.com/640112/the-career-advice-no-one-tells-you/)]
- Wanted in College Graduates: Tolerance for Ambiguity. [[Linkedin Pulse](https://www.linkedin.com/pulse/wanted-college-graduates-tolerance-ambiguity-jeff-selingo)]
- How to set goals: OKRs. [[Youtube](https://www.youtube.com/watch?v=mJB83EZtAjc)]
- Meetings that don’t suck. [[Youtube](https://www.youtube.com/watch?v=rU8nv38E0Qk)]

@@

- Data Pitfalls —the Startup Edition. [[Medium](https://medium.com/@mrogati/data-pitfalls-the-startup-edition-fe1eebcc39da#.si84k3dss)]

@@

- 'Amazon is not your friend'. [[Linkedin](https://www.linkedin.com/pulse/amazon-your-friend-caroline-fairchild)]
    - The only way to survive is to build a brand that can grow without Amazon’s distribution.
    - Amazon hasn’t proven that it can build inspirational brands. While they have mastered the ability to get customers commodity products, no one goes to Amazon to discover something they didn’t already know about.
- Facebook is the new Excel. [[blog](http://alexmuir.com/facebook-is-the-new-excel)]
- We need companies to start innovating instead of imitating success stories. [[Hustle](http://thehustle.co/snapchat-vs-spacex-battle-of-the-imitators-and-innovators)]
- My 4+ Years At Uber Taught Me These Key Lessons. 1. May the supply be with you ; 2. Don't listen, show them. [[Linkedin](https://www.linkedin.com/pulse/three-things-i-learned-during-4-years-uber-michael-pao)]

### 2016-05-24 bayesian_statistics/MCMC/MCMC.Rmd
bandits 1
completely reorganized

*Markov Chain Monte Carlo (MCMC)* is a class of methods in which we can simulate draws (taking samples) that are slightly dependent and are approximately from a (posterior) distribution. We then take those draws and calculate quantities of interest for the (posterior) distribution. Here, we'll bw attempting to give you an intuition behind one branch of the MCMC sampling, namely the **Metropolis–Hastings Algorithm**.

@@

			# propose a new sample point (will elaborate on this later)			
			proposal <- sample + rnorm( n = 2, mean = 0, sd = 1 )

>>>>

*Markov Chain Monte Carlo (MCMC)* is a class of methods in which we can simulate draws (taking samples) that are slightly dependent and are approximately from a (posterior) distribution. We then take those draws and calculate quantities of interest for the (posterior) distribution. Here, we'll be attempting to give you an intuition behind one branch of the MCMC sampling, namely the **Metropolis–Hastings Algorithm**.

@@

			# propose a new sample point		
			proposal <- sample + rnorm( n = 2, mean = 0, sd = 1 )
